Through the eyes of the teacher

### 2022-05-04 02_paper/01_pilot/paper_1_supplement_questionnaire.Rmd
update workflow liste

# calculate Cronbach's Alpha for each scale
# activation & support
self.as.wide <- quest.raw.data %>%
                          filter (scale == "Activation and support") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)
self.alpha.as <- alpha(self.as.wide[,-1])

#clarity & structuredness
self.cs.wide <- quest.raw.data %>%
                          filter (scale == "Clarity and structuredness") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#classroom management
self.cm.wide <- quest.raw.data %>%
                          filter (scale == "Classroom management") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#natural behaviour
self.nb.wide <- quest.raw.data %>%
                          filter (scale == "Natural behaviour") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#positive climate and motivation
self.pcm.wide <- quest.raw.data %>%
                          filter (scale == "Positive climate and motivation") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#presence: posture & gaze
self.ppg.wide <- quest.raw.data %>%
                          filter (scale == "Presence: posture/gaze") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#presence: voice
self.pv.wide <- quest.raw.data %>%
                          filter (scale == "Presence: voice") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#presence: verbal/non-verbal intervention
self.pvni.wide <- quest.raw.data %>%
                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#Presence without subscales
self.p.wide <- quest.raw.data %>%
                          filter(str_detect(scale,
                                        paste(c(
                                        "Presence: voice", 
                                        "Presence: verbal and non-verbal intervention", 
                                        "Presence: posture/gaze"),
                                         collapse = '|'))) %>% 
                          select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

# # item analysis of a scale or index using the tab_itemscale() function of the sjPlot package
# 
# # activation & support
# tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # classroom management
# tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # clarity & structuredness
# tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # natural behaviour
# tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # postive clima and motivation
# tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # presence without subscales
# tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# 
# # presence: posture & gaze
# tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# # presence: voice
# tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# # presence: verbal/non-verbal intervention
# tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

>>>>

# calculate Cronbach's Alpha for each scale
# activation & support
self.as.wide <- quest.raw.data %>%
                          filter (scale == "Activation and support") %>%  
                          dplyr::select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)
self.alpha.as <- alpha(self.as.wide[,-1])

#clarity & structuredness
self.cs.wide <- quest.raw.data %>%
                          filter (scale == "Clarity and structuredness") %>%  
                          dplyr::select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#classroom management
self.cm.wide <- quest.raw.data %>%
                          filter (scale == "Classroom management") %>%  
                          dplyr::select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#natural behaviour
self.nb.wide <- quest.raw.data %>%
                          filter (scale == "Natural behaviour") %>%  
                          dplyr::select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#positive climate and motivation
self.pcm.wide <- quest.raw.data %>%
                          filter (scale == "Positive climate and motivation") %>%  
                          dplyr::select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#presence: posture & gaze
self.ppg.wide <- quest.raw.data %>%
                          filter (scale == "Presence: posture/gaze") %>%  
                          dplyr::select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#presence: voice
self.pv.wide <- quest.raw.data %>%
                          filter (scale == "Presence: voice") %>%  
                          dplyr::select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#presence: verbal/non-verbal intervention
self.pvni.wide <- quest.raw.data %>%
                          filter (scale == "Presence: verbal and non-verbal intervention") %>%  
                          dplyr::select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

#Presence without subscales
self.p.wide <- quest.raw.data %>%
                          filter(str_detect(scale,
                                        paste(c(
                                        "Presence: voice", 
                                        "Presence: verbal and non-verbal intervention", 
                                        "Presence: posture/gaze"),
                                         collapse = '|'))) %>% 
                          dplyr::select(shortID, value) %>%
                          group_by(shortID) %>%
                          mutate(id=row_number()) %>%
                          spread(shortID, value)

@@

# activation & support
tab_itemscale(self.as.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

# classroom management
tab_itemscale(self.cm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

# clarity & structuredness
tab_itemscale(self.cs.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

# natural behaviour
tab_itemscale(self.nb.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

# postive clima and motivation
tab_itemscale(self.pcm.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

# presence without subscales
tab_itemscale(self.p.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)

# presence: posture & gaze
tab_itemscale(self.ppg.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# presence: voice
tab_itemscale(self.pv.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
# presence: verbal/non-verbal intervention
tab_itemscale(self.pvni.wide[,-1], show.shapiro = TRUE, show.kurtosis = TRUE)
